---
title: "Titanic_Solution"
author: "Pranjal Vijay"
date: "March 2, 2018"
output: html_document
---
```{r}
#Load the libraries
library(ggplot2)
library(dplyr)
library(statsr)
```
```{r}
#Load the Data
Traindataset<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Titanic_survived/train.csv", stringsAsFactors = F)
Testdataset<-read.csv("C:/Users/ddddd/Comptitions/Kaggle/Titanic_survived/test.csv", stringsAsFactors = F)
```
###Research Question: 
According to the provided data of Titanic Disaster we are asked to find out the information of people who survived . 

Observing the given data sets , I found these variables more impactable:
Survived , Sex and Age.

I am going to calculate here that who survived more :

(i)  Males or Females 

(ii) People below or above average age 

##Data Exploration
```{r}

names(Traindataset)
```
```{r}
str(Traindataset)
```

##Data Preprocessing

####How many males and female on Titanic ?
```{r}
Traindataset %>% 
  filter(Sex != "NA") %>%
  group_by(Sex) %>% 
  summarise(count = n())
```

####People having age 
```{r}
Traindataset$Age <- as.integer(Traindataset$Age)
```

```{r}
Traindataset %>% 
  filter(Age != "NA") %>%
 mutate(Age = ifelse(Age > 0, "Positive_Sur", "Negative_Sur"))
Traindataset %>%  
  group_by(Age) %>% 
  summarise(count = n())
```
```{r}
Traindataset %>% 
  filter(!(is.na(Age))) %>%
  summarise(Agemean = mean(Age), Agemedian = median(Age), Agesd = sd(Age), 
            Agemin = min(Age), Agemax = max(Age))
```
```{r}
Traindataset <- Traindataset %>% 
    filter(!(is.na(Age))) %>%
   mutate(Age = ifelse(Age >= 28, "HighAge", "LowAge"))
Traindataset %>% 
  group_by(Age) %>% 
  summarise(count = n())
```




```{r}
Traindataset <- Traindataset %>% 
    filter(!(is.na(Survived))) %>%
  mutate(Survived = ifelse(Survived > 0, "Positive_Sur", "Negative_Sur"))
Traindataset %>% 
  group_by(Survived) %>% 
  summarise(count = n())
```


```{r}
Traindataset$Fare <- as.factor(Traindataset$Fare)
Traindataset %>% 
  filter(Fare != "NA") %>%
  group_by(Fare) %>% 
  summarise(count = n())
```


